Suboptimal Time management in Non-ideal Shared space

### 2015-04-12 paper.tex
More to Existing Literature and a New section

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Need for Suboptimal Time management in Non-ideal Shared space}

@@

\begin{abstract}
%\boldmath
Time management is an asset and a liability. Lack of proper time management may put oneself on a depression feedback loop [1]. Time management is a melange of various aspects - scheduling tasks, execution and time line corrections, to name a few. Each of these aspects can be thought as a subproblem in our attempts to tackle the grand problem - Optimal Time Management. In addition to these subproblems, we must accept the fact that we live in a non-ideal world along with many others - shared space.  The paper deducts the need for an adaptive, suboptimal Time Management techniques taking external stimulus into consideration.
\end{abstract}

@@

\section{Introduction}
% \IEEEPARstart
Time and Time Management are of paramount importance. This brings in an obvious urge to develop various techniques for an optimal time management technique. Starting from marking calender to a rigid time plan accounting for each hour of a day. There are a whole lot of techniques to make a basic plan, some of which will be covered in the existing literature section. One major aspect of time management is making a perfect schedule but an even more crucial part kicks in during its execution. There are several factors that could keep one from meeting their time plan. Stress, Bad planning, Lack of self control etc., which are mostly internal factors - in the sense that their correction is solely dependent on the individual. There are also external factors that could affect ones time plan - factors which the individual may not have anticipated or predicted at the time of planning.

The source of all the factors that affect time plans, broadly speaking, are a result of the fact that we live in a shared space where we are affected not only by our own actions but also by the choices of those around us and that we live in a non-ideal world where most events are probability based, not guided by any standard Uncertainty Principle, brings in more players into the equation. All these complex parameters would push any purely mathematical or conceptual approach to derive an optimal time plan into solving an NP-Hard problem [2]. One has to live with a suboptimal time plan for a given situation, iterate it based on their needs and arrive at an acceptable compromise between an ideal and executable plan.

The following contents of the paper are divided into four sections. Section II - Existing literature, would focus on some of the existing techniques for Time management. Followed by Section III - Execution and Evaluation, which is completely spanned by a case study where the subject employs an adaptive time management technique for their day to day activity for two fortnights. We will then conclude with Section IV - Conclusions, where would be highlighting the key aspects of our argument and how we derived or observed them in the case of the test subject.

\section{Existing literature}
There is plethora of research related to Time Management (TM) techniques and surveys depicting the outcomes of adopting or otherwise of a TM technique. [3], [4] and [5] centered their work around the impact of TM in an academic context, backing their claims through surveys with varying size of sample space and interpretations but similar outcomes. Time Management behaviors may have beneficial effects on tensions and job satisfaction but not on job performance. Contrary to popular claims, time management training was not found to be effective [6]. This controverts the hypothesis and findings of [7] and [8].

@@

Some of the very common time management methodologies are Pareto analysis, ABC analysis and The Eisenhower Method. The central idea of Pareto analysis is that 80\% of tasks can be completed in 20\% of the disposable time - The 80-20-rule to increase productivity [12]. ABC analysis is often used in business management for categorization of large data into groups [11]. These groups are often marked A -- Tasks that are perceived as being urgent and important, B -- Tasks that are important but not urgent, and C -- Tasks that are neither urgent nor important. Each group is then rank-ordered by priority. Last in our list, The Eisenhower Method, uses the Eisenhower Decision Principle through which, all tasks are evaluated using the criteria important/unimportant and urgent/not urgent, and then placed in according quadrants in an Eisenhower Matrix as shown in figure 1.

@@

@@

\begin{figure}[hb]
  \centering
  \includegraphics[width=3.7in]{bar}
  \caption[]
   {Hours spent per activity in a week for a period of four weeks}
\end{figure}

@@

\bibitem{IEEEhowto:}
Misra, Ranjita, and Michelle McKean. \emph{"COLLEGE STUDENTS'ACADEMIC STRESS AND ITS RELATION TO THEIR ANXIETY, TIME MANAGEMENT, AND LEISURE SATISFACTION."} American Journal of Health Studies 16.1 (2000): 41-51.

@@

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Suboptimal Time management in Non-ideal Shared space}

@@

\begin{abstract}
%\boldmath
Time management is an asset and a liability. Lack of proper time management may put oneself on a depression feedback loop [1]. Time management is a melange of various aspects - scheduling tasks, execution and time line corrections, to name a few. Each of these aspects can be thought as a subproblem in our attempts to tackle the grand problem - Optimal Time Management. In addition to these subproblems, we must accept the fact that we live in a non-ideal world along with many others - shared space.  The paper deducts the need for adaptive, suboptimal Time Management techniques while taking external stimuli into consideration.
\end{abstract}

@@

\section{Introduction}
% \IEEEPARstart
Time and Time Management are of paramount importance. This brings in an obvious urge to develop various techniques for an optimal time management technique - starting from marking calenders to a rigid time plan accounting for each hour of a day. There are a whole lot of techniques to make a basic plan, some of which will be covered in the existing literature section. One major aspect of time management is making a perfect schedule but an even more crucial step concerns with the execution. There are several factors that could keep one from meeting their time plan. Stress, Bad planning, Lack of self control and so on so forth.

The source of all the factors that affect time plans, broadly speaking, are a result of the fact that we live in a shared space where we are affected not only by our own actions but also by the choices of those around us, and that we live in a non-ideal world where most events are probability based, not guided by any standard Uncertainty Principle, thus bringing in more players into the equation. All these complex parameters would push any purely mathematical or conceptual approach to derive an optimal time plan into solving an NP-Hard problem [2]. One has to live with a suboptimal time plan for a given situation, iterate it based on their needs and arrive at an acceptable compromise between an ideal and a executable plan.

The following contents of the paper are divided into four sections. Section II - Existing literature, would focus on some of the existing techniques for Time management. Followed by Section III - Identifying factors, where we identify a list of factors that could affect ones time plan and identify plausible ways to workaround them. Section IV - Execution and Evaluation, which is completely spanned by a case study where the subject employs an adaptive time management technique for their day to day activity for two fortnights and we would discuss the outcomes of the experiment in light of the existing and proposed theory. We will then conclude with Section V - Conclusions, where would be highlighting the key aspects of our argument and how it compared to our observations in the case of the test subject.

\section{Existing literature}
There is plethora of research related to Time Management (TM) techniques and surveys depicting the outcomes of adopting or otherwise of a TM technique. [3], [4] and [5] centered their work around the impact of TM in an academic context, backing their claims through surveys with varying size of sample space and interpretations but similar outcomes. [6], in contrary to the above mentioned research, suggests that Time Management behaviors may have beneficial effects on tensions and job satisfaction but not on job performance and contrary to popular claims, time management training was not found to be effective. This also controverts the hypothesis and findings of [7] and [8]. There is plenty on existing and ongoing research related to the identification of the nature and magnitude of the affects Time management has on its subjects

@@

Some of the common time management methodologies are Pareto analysis, ABC analysis, The Eisenhower Method and POSEC method. The central idea of Pareto analysis is that 80\% of tasks can be completed in 20\% of the disposable time - The 80-20-rule to increase productivity [12]. ABC analysis is often used in business management for categorization of large data into groups [11]. These groups are often marked A -- Tasks that are perceived as being urgent and important, B -- Tasks that are important but not urgent, and C -- Tasks that are neither urgent nor important. Each group is then rank-ordered by priority. On the other hand, The Eisenhower Method uses the Eisenhower Decision Principle through which, all tasks are evaluated using the criteria important/unimportant and urgent/not urgent, and then placed in according quadrants in an Eisenhower Matrix as shown in figure 1. Last in our list, POSEC method is an acronym for Prioritize by Organizing, Streamlining, Economizing and Contributing. Inherent in the acronym is a hierarchy or priority of task ordering. Prioritize -- Defining goals, Organize -- Things one has to accomplish regularly, Streamline -- Things one may not like but must do anyway, Economize -- Things one likes to do but not pressing and finally, Contribute -- The left over tasks that make a difference.

All the methods we discussed earlier are theoretical constructs which suggest various ways we could opt to manage time or tasks. Since we live in a digital world, it is a natural tendency to seek computer-aided tools - Desktop, Smart phone or Web applications, that can help follow a schedule of choice in a more convenient fashion. There are in fact many software tools that have already integrated one or more of the above techniques and available on the App stores. However, only a small portion of them are actually developed out of independent academic research. These computer-aided task or time tracking tools are often a good way for tracking or analyzing the time plans and also simplifies the job of identifying the short comings. [14] is one such multi purpose tools which, in addition to location tracking, also offers activity logging and tagging. This actually leads to a better contextual information on the activity and its progress.

@@

\section{Identifying factors}
There are a plethora of factors that could disrupt a time plan and they can be broadly categorized into External and Internal factors. Internal factors are those that solely dependent on the individual or arise as an outcome to an individuals actions. While External factors are the ones which the individual may not have anticipated or predicted at the time of planning and mostly a result of the actions of external entities.

\textbf{Internal factors:} Some common examples of Internal factors are Stress, Bad planning, Lack of self control and Addictions, all of which are outcomes of a person's own shortcomings. These are the ones which are entirely under the control of the individual - attempting to follow a routine, alone. More often than not, these factors can be corrected by having a greater perseverance, self control and dedication on the part of the person following or trying to follow a routine. Some of the other tricks that could work is developing habits out of the plan - Motivation is what gets them started while habit is what keeps them going.

\textbf{External factors:} These on the other hand are those which cannot be controlled by the individual alone. Most commonly, external factors occur as a consequence, either direct or indirect and deliberate or unintentional, actions of those around the subject. Due to the very nature of the cause of these factors, the countermeasures are not as uncomplicated as the Internal factors. Often times they are hard to prevent within the control of the subject. So, the next best and feasible approach to tackling External factors is to employ appropriate degree of flexibility in the time plans to alleviate the possible damage. Identifying the source of these factors could often assist in estimating a suitable level of flexibility that should be incorporated into the plan.

@@

\begin{figure}[hb]
  \centering
  \includegraphics[width=3.7in, height=3.0in]{bar}
  \caption[]
   {Hours spent per activity in a week for a period of four weeks}
\end{figure}

@@

\bibitem{IEEEhowto:}
Misra, Ranjita, and Michelle McKean. \emph{"College Students' Academic stress and its relation to their Anxiety, Time Management, and Leisure satisfaction."} American Journal of Health Studies 16.1 (2000): 41-51.

@@

\bibitem{IEEEhowto:}
Schweizer, Immanuel, and Benedikt Schmidt. \emph{"Kraken. me: multi device	 user tracking suite."} Proceedings of the 2014 ACM International	Joint Conference on Pervasive	and	Ubiquitous Computing: Adjunct Publication. ACM, 2014.
